Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
remove hyperlink and add real reference

\documentclass{acm_proc_article-sp}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}

@@

\hypertarget{the-translation-process}{}
\subsection{The translation process}
\label{translationprocess}

@@

\subsection{Building control flow graphs}
\label{flowobjspace}
\hypertarget{flowobjspace}{}

As described in the overview of \href{\#the-translation-process}{the
translation process}, the front-end of the translation tool-chain
works in two phases: it first builds control flow graphs from Python
functions, and then performs whole-program type inference on these
graphs.

@@

Here is a simplified, static model of how the annotator works.  It can
be considered as taking as input a finite family of functions calling
each other, and working on the control flow graphs of each of these
functions as built by the \href{flowobjspace}{Flow Object Space}.
Additionally, for a particular "entry point" function, the annotator
is provided with user-specified types for the function's arguments.

>>>>

\documentclass{acm_proc_article-sp}

@@

\subsection{The translation process}
\label{translationprocess}

@@

\subsection{Building control flow graphs}
\label{flowobjspace}

As described in the overview of the translation process (section
\ref{translationprocess}), the front-end of the translation tool-chain works in
two phases: it first builds control flow graphs from Python functions, and then
performs whole-program type inference on these graphs.

@@

Here is a simplified, static model of how the annotator works.  It can
be considered as taking as input a finite family of functions calling
each other, and working on the control flow graphs of each of these
functions as built by the Flow Object Space (section \ref{flowobjspace}).
Additionally, for a particular "entry point" function, the annotator
is provided with user-specified types for the function's arguments.
